The Impact of Anthropogenic Forcing on ENSO Amplitude

### 2021-08-20 presentations/presentation/presentation.tex
Presentation i use tikz!!!

\documentclass{beamer}
\title{The Impact of Anthropogenic Forcing on ENSO Amplitude}
\author{Ben Goldman}
\date{\today}
\usepackage{natbib}
\usepackage{tikz}
\usetheme{metropolis}
\renewcommand{\bibsection}{}
\setbeamerfont{caption}{size=\tiny}

@@

  \begin{columns}
    \column{0.4\textwidth}
    \begin{itemize}
    \item The earth is getting warmer. \citep{pachauri2014climate}
    \item Climate varies on different scales.
    \item Long-term trends and short-term noise.
    \end{itemize}
    \column{0.6\textwidth}
    \myfig{intro_fig_3.pdf}{Global mean land air temperature in GISSTEMP 4 dataset. \citep{gistemp2019giss} and \citep{lenssen2019improvements}}{this}
  \end{columns}
\end{frame}

@@

@@

\begin{frame}{Measuring ENSO}

@@

@@

\begin{frame}{It's not That Simple}

@@

\begin{frame}{Stratification in Other Ensembles}

>>>>

\documentclass{beamer}
\title{The Impact of Anthropogenic Forcing on ENSO Amplitude}
\author{Ben Goldman}
\date{\today}
\usepackage{natbib}
\usepackage{tikz}
\usepackage{varwidth}
\usetikzlibrary{arrows,snakes,backgrounds}
\usetheme{metropolis}
\renewcommand{\bibsection}{}
\setbeamerfont{caption}{size=\tiny}

@@

  \begin{columns}
    \column{0.6\textwidth}
    \begin{itemize}
    \item The earth is getting warmer. \citep{pachauri2014climate}
    \item Climate varies on different scales.
    \item Long-term trends and short-term noise.
    \item Forcing: any external factor that affects climate
      \begin{itemize}
      \item Greenhouse gasses
      \item Aerosols (natural: volcanic ash, artificial: smoke)
      \item Biomass burning
      \item Land use/cover (deforestation, desertification)
      \end{itemize}
    \end{itemize}
    \column{0.4\textwidth}
    \myfig{intro_fig_3.pdf}{Global mean land air temperature in GISSTEMP 4 dataset. \citep{gistemp2019giss} and \citep{lenssen2019improvements}}{this}
  \end{columns}
\end{frame}

@@

  \begin{tikzpicture}[node distance = 1.5in, thick]

    \node (input) [rectangle, draw] {
      \begin{varwidth}{1.5in}
        Independent variables
        Ex. greenhouse gas
      \end{varwidth}};

    \node (model) [right of=input, circle, draw] {
      \begin{varwidth}{\linewidth}
        Computer\\Simulation
      \end{varwidth}};

    \node (output) [right of=model, rectangle, draw] {
      \begin{varwidth}{1.4in}
        Dependent variables
        Model's predictions
      \end{varwidth}};

    \draw [->] (input.east) -- (model.west);
    \draw [->] (model.east) -- (output.west);

  \end{tikzpicture}

@@

\begin{frame}{Model Setup}
  Input:
  \begin{itemize}
  \item Observed forcing levels from 1850-2005
  \item Predicted forcing levels from 2005-2100
  \item \textbf{Simulation ran a total of 40 times with slightly different starting point}
  \item Control simulation with pre-1850 forcing levels
  \end{itemize}
  Model:
  \begin{itemize}
  \item CESM1 \citep{kay2015community}
  \item CESM2 \citep{danabasoglu2020community}
  \end{itemize}
  Output: Sea Surface Temperature (SST)
\end{frame}

@@

  \tikzstyle{process}=[circle, draw=black!50,fill=black!20, line width = 0.2mm]
  \tikzstyle{data}=[rectangle, draw=blue!50,fill=blue!20, line width = 0.2mm]
  \begin{tikzpicture}[node distance = 1.5in, line width = 0.5mm]

    \node [data] (input) {
      \begin{varwidth}{1.5in}
        External forcing
      \end{varwidth}};

    \node [process] (model) [right of=input] {
      \begin{varwidth}{\linewidth}
        CESM1\\and\\CESM2
      \end{varwidth}};

    \node [data] (output) [right of=model] {
      \begin{varwidth}{1.2in}
        Sea surface temperature (SST)
      \end{varwidth}};

    \node [data] (nino) [below of=input] {
      \begin{varwidth}{1.4in}
        Niño 3.4 index
      \end{varwidth}};

    \node [process] (variance) [right of=nino] {
      \begin{varwidth}{1.4in}
        Windowed\\variance
      \end{varwidth}};

    \node [data] (intensity) [right of=variance] {
      \begin{varwidth}{1.4in}
        ENSO intensity
      \end{varwidth}};

    \draw [->] (input) to (model);
    \draw [->] (model) to (output);
    \draw [->] (output) to [out = 270, in = 90] (nino);
    \draw [->] (nino) to (variance);
    \draw [->] (variance) to (intensity);

  \end{tikzpicture}

@@

@@
